



```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```


```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest) # to scrape wikipedia page
```



# Where Do People Drink The Most Beer, Wine And Spirits?

Back in 2014, [fivethiryeight.com](https://fivethirtyeight.com/features/dear-mona-followup-where-do-people-drink-the-most-beer-wine-and-spirits/) published an article on alchohol consumption in different countries. The data `drinks` is available as part of the `fivethirtyeight` package. Make sure you have installed the `fivethirtyeight` package before proceeding.


```{r, load_alcohol_data}
library(fivethirtyeight)
data(drinks)


# or download directly
# alcohol_direct <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/alcohol-consumption/drinks.csv")

```


What are the variable types? Any missing values we should worry about?


```{r glimpse_skim_data}
# YOUR CODE GOES HERE
glimpse(drinks)
skim(drinks)

```


Make a plot that shows the top 25 beer consuming countries

```{r beer_plot}
# YOUR CODE GOES HERE
drinks %>%
  slice_max(order_by = beer_servings, n=25)%>%
  mutate(country = fct_reorder(country,beer_servings))%>%
  ggplot(aes(y=country, x=beer_servings))+
  geom_col(fill = 'yellow')+
  labs(title = "Where do people drink more beer?",
         subtitle = "--",
         x = "beer_servings", 
         y = "country",
         caption = "Source: https://github.com/nytimes/covid-19-data")+
  NULL
  

```

Make a plot that shows the top 25 wine consuming countries

```{r wine_plot}

# YOUR CODE GOES HERE
drinks %>%
  slice_max(order_by = wine_servings, n=25)%>%
  mutate(country = fct_reorder(country,wine_servings))%>%
  ggplot(aes(x=wine_servings, y=country))+
  geom_col()
  NULL

```

Finally, make a plot that shows the top 25 spirit consuming countries
```{r spirit_plot}
# YOUR CODE GOES HERE
drinks %>%
  slice_max(order_by = spirit_servings, n=25)%>%
  mutate(country = fct_reorder(country,spirit_servings))%>%
  ggplot(aes(y=country, x=spirit_servings))+
  geom_col()
  NULL
```

